\begin{thebibliography}{99}
    \bibitem{ata-5}
        T13 Committee.
        \textit{Information Technology - AT Attachment with Packet Interface - 5 (ATA/ATAPI-5)}.
        Februar 2000.
        \url{https://web.archive.org/web/20110728081430/http://www.t10.org/t13/project/d1321r3-ATA-ATAPI-5.pdf}

    \bibitem{ata-6}
        T13 Committee.
        \textit{Information Technology - AT Attachment with Packet Interface - 6 (ATA/ATAPI-6)}.
        Dezember 2001.
        \url{https://web.archive.org/web/20110728081452/http://www.t10.org/t13/project/d1410r3a-ATA-ATAPI-6.pdf}

    \bibitem{pollard2011}
        Jonathan de Boyne Pollard.
        \textit{The gen on disc partition alignment}.
        \url{http://jdebp.eu/FGA/disc-partition-alignment.html}
        Zuletzt abgerufen am 19.11.2020.

    \bibitem{uuid-rfc}
        P. Leach, Microsoft, M. Mealling, Refactored Networks LLC, R. Salz, DataPower Technology Inc.
        \textit{Request for Comments: 4122 - A Universally Unique IDentifier (UUID) URN Namespace}.
        Juli 2005.
        \url{https://tools.ietf.org/html/rfc4122}

    \bibitem{uefi-spec}
        UEFI Forum.
        \textit{UEFI Specification Version 2.8 (Errata A)}.
        Februar 2020.
        \url{https://www.uefi.org/specifications}

    \bibitem{mbr-4tb-workaround}
        Rod Smith.
        \textit{Working Around MBR's Limitations}.
        \url{http://www.rodsbooks.com/gdisk/workarounds.html}
        Zuletzt abgerufen am 21.11.2020.

    \bibitem{drive-partition-limits}
        UEFI Forum.
        \textit{FAQ: Drive Partition Limits}.
        2010.
        \url{https://www.uefi.org/sites/default/files/resources/UEFI_Drive_Partition_Limits_Fact_Sheet.pdf}


    \bibitem{linux-kernel-genhd}
        Linux kernel developers.
        \textit{genhd.h}.
        \url{https://git.kernel.org/pub/scm/linux/kernel/git/efi/efi.git/tree/include/linux/genhd.h}
        Zuletzt abgerufen am 10.12.2020.

    \bibitem{windows-gpt}
        Microsoft.
        \textit{Windows and GPT FAQ}.
        \url{https://docs.microsoft.com/en-us/windows-hardware/manufacture/desktop/windows-and-gpt-faq}
        Zuletzt abgerufen am 10.12.2020.

    \bibitem{heise-mbr-gpt}
        Mirco Lang, Heise.
        \textit{Festplatten-Partitionen: MBR oder GPT? Tipps \& Tricks.}
        \url{https://www.heise.de/tipps-tricks/Festplatten-Partitionen-MBR-oder-GPT-4351715.html}
        Zuletzt abgerufen am 12.12.2020.

    \bibitem{wikipedia-crc}
        Wikipedia.
        \textit{Cyclic redundancy check}
        \url{https://en.wikipedia.org/wiki/Cyclic_redundancy_check}
        Zuletzt abgerufen am 13.12.2020.
\end{thebibliography}
